\documentclass{article}
\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{textgreek}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[scaled=1]{berasans}
\usepackage[T1]{fontenc}

\pagenumbering{gobble}
\renewcommand{\labelitemi}{$-$}

\begin{document}
\center{\Large\bf Ali Kakakhel}
\vskip2mm
\hrule
\center{2104 \ \ 59th \ \ Ave \ \ Ct \ \ Greeley, \ \ CO \ \ 80634 \quad\qquad alikakakhel@yahoo.com \quad\qquad (970) 396-5137\\\ \\}

\begin{description}[leftmargin=!,labelwidth=3cm]

\item[Objective]
An audit internship position for Jan -- May 2017.

\item[Education]
{\sl Master's of Accounting} \hfill Dec 2017\\
University of Northern Colorado, Greeley, CO

{\sl Bachelor's of Business Administration, Accounting} \hfill Dec 2016\\
University of Northern Colorado, Greeley, CO\\
Accounting GPA: 3.8 \qquad\ \  Overall GPA: 3.85

{\sl Masters of Science, Radiological Physics} \hfill May 2012\\
Wayne State University, Detroit, MI\\
GPA: 3.43

{\sl Bachelor of Science, Physics} \hfill May 2008\\
Colorado State University, Fort Collins, CO \\
Minor: Mathematics\\
GPA: 3.787

\item[Experience]
{\sl Data Analyst Intern} \hfill June 2016 -- July 2016\\North Colorado Medical Center
\begin{itemize}[rightmargin=4.3cm]
    \item Expanded the Python program to save results to a PostgreSQL database for future querying.
    \item Developed dashboard to display and filter treatment plan quality results against various criteria.
\end{itemize}

{\sl Professional Tutor} \hfill Jan 2013 -- Present\\Aims Community College
\begin{itemize}[rightmargin=4.3cm]
    \item Accounting, Math, Physics, Programming, Statistics
\end{itemize}

{\sl Data Entry Volunteer} \hfill May 2013 -- Present\\North Colorado Medical Center
\begin{itemize}[rightmargin=4.3cm]
    \item Prepared data tables used by dosimetrists in treatment planning.
    \item Developed a Python program to process treatment plan data into various quality measures.
    \item Developed dashboard, spreadsheet to track treatment timelines.
    \item Developed dashboard, spreadsheet to track wait times.
    \item Developed process for 3D printing patient specific compensators.
    \item Assisted in commissioning of new TrueBeam Linear Accelerator.
    \item Assisted in daily, monthly, annual Linear Accelerator quality \\ assurance.
\end{itemize}

\item[Leadership]
Beta Alpha Psi (BAP)\ \ Community Service Officer \hfill Fall 2016\\
Society of Physics Students\ \ Vice-President \hfill Fall 2007, Spring 2008

\item[Awards]
US President's Volunteer Service Award \hfill Summer 2016\\
BAP\ \ Gold Member \hfill Spring 2016\\
BAP\ \ Community Service Award \hfill Spring 2016\\
BAP\ \ Community Service Award \hfill   Fall 2015\\
Dean's Citation for Academic Excellence \hfill Fall 2015

\item[Tools]
Access\ \ \ Excel\ \ \ Matlab\ \ \ PostgreSQL\ \ \ Tableau

\item[Languages]
ACL\ \ \ C/C++\ \ \ JSON\ \ \ Python\ \ \ R\ \ \ SQL\ \ \ XBRL\ \ \ XML\\\ \\

% \item[Productivity]
% Microsoft Office, LibreOffice\\
% Ledger, Beancount (open source plain text accounting)\\
% OpenERP (open source ERP software)\\
% LaTeX (open source professional publishing software)

% \item[References]\ \\\ \\
% % \hskip-\labelwidth
% \vskip-7.5mm
% \hskip-2mm
% \begin{tabular}{lll}
% Nike Rovero         & Alex Markovic            & Jon Baldwin             \\
% Tutoring Supervisor & Intership Supervisor     & Volunteering Supervisor \\
% (970) 339-6283      & (970) 396-2201           & (970) 392-6692          \\
% veronica.rovero     & alexander.markovic       & jonathan.baldwin        \\
% @aims.edu           & @bannerhealth.com        & @bannerhealth.com       
% \end{tabular}

\end{description}

\end{document}